Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-01 article.qmd
Remove pdf and docx outputs

---
title: "Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems."
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
    css: article.css
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
  docx:
    number-sections: true
---

>>>>

---
title: "Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems."
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
    css: article.css
---
